---
title: "Fars Functions"
author: "Josef Tapper"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fars Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is the vignette documentation for the Corusera Week 4 exercise.

## Functions
#### fars_read
This function takes a path as a parameter reads the file into a data.frame object.\n
```{r fars_read_chunk, echo=TRUE}
df<-CourseraWeek2::fars_read(CourseraWeek2::make_filename(2013))
head(df)
```

#### make_filename
This function takes an integer representing the year and returns a string formatted to match the filename of the file for that year.\n

```{r make_filename_chunk, echo=TRUE }
CourseraWeek2::make_filename(2013)
```

#### fars_read_years
This function takes a list of years,and reads the data from the corresponding files into a single dataset.\n

```{r fars_read_years_chunk,echo=TRUE}
df<-CourseraWeek2::fars_read_years(c(2013,2014))
head(df)
```

#### fars_summarize_years
This function takes a list of years as a parameter and uses it to build the filenames for those years
based on the appropriate naming convetion to generate a dataframe of the years and months of each accident summarised by month with each year as a separate variable.\n

```{r fars_summarize_years_chunk,echo=TRUE }
CourseraWeek2::fars_summarize_years(c(2013,2014))
```

#### fars_map_state
This function generates a map of the state with the location of the accidents. It uses parameters of state number and year.\n

```{r fars_map_state_chunk, eval=FALSE, include=FALSE}
 CourseraWeek2::fars_map_state(10,2014)
```
I would put a map here but the maps package is a bit dodgy. It will run OK in the RStudio, but crashes when you Knit. This is a documented error with no solution...but it made it to CRAN. (Probably with the dontrun option)

